\capitulo{2}{Project Objectives}
This chapter defines the objectives pursued by the project. The main purpose of this study is: to use Artificial Neural Networks (ANNs) as an alternative for sky classification by the CIE standard, as well as exploring different training functions for the Artificial Neural Network.
\subsection{General Objectives}
\begin{enumerate}
	\item Investigate the applicability of using ANNs for sky classification under the CIE standard.
	\item Use different training functions for the network and compare their performance metrics.
    \item Evaluate whether other training functions aside from the Scaled Conjugate Gradient are a viable option for sky classification ANNs.
    \item Evaluate the performance of using one of the highest scoring image-processing methods from previous research \cite{skyClassANN-Granados-Lopéz}, with the aforementioned training functions.
\end{enumerate}
\subsection{Technical Objectives}
\begin{enumerate}
    \item Research the basics of sky classification and its use cases.
    \item Setup sky image dataset provided by the UBU in such a way that it may be used for ANNs.
    \item Load the images into the ANN working environment.
    \item Resize images into an even format, so that its computational cost is not too high to not be usable.
    \item Extract class labels using the Matlab Deep Learning Toolbox.
    \item Choose multiple training functions that focus on the usage of backpropagation.
    \item Train the network using each training function and a different combination of training parameters and compare the results.
    \item Perform the training again, but this time with image-processing technique applied (the panchromatic channel of each image).
    \item With the acquisition of passable results, execute training and testing of the network again, this time using cross-validation.
    \item Extract network variation with the best performance.
\end{enumerate}
\subsection{Personal Objectives}
\begin{enumerate}
    \item Apply my knowledge acquired about Artificial Intelligence and Neural Networks throughout my exchange semester here through the Computer Engineering Degree.
    \item Further deepen my knowledge on using the Matlab Deep Learning Toolbox for the development of Artificial Neural Networks.
    \item Delve into the field of sky classification and its use cases.
    \item Deepen my understanding of ANNs and the training parameters.
    \item Learn more about pattern recognition and its application using supervised machine learning.
    \item Expand my understanding of multi-class classification problems and their implementation using pattern networks.
\end{enumerate}
\subsection{Report Structure}
The report structure is given below, to give a short overview of the content of each chapter
\begin{itemize}
    \item Introduction: a short summary of the purpose and motivation for this project
	\item Objectives: the desired goals and purposes of the project are specified, both on a general and technical level, as well as a personal level.
	\item Theoretical Concepts: a short inauguration into the basic concepts that will be discussed in this project, mostly in regards to ANNs.
    \item Techniques and Tools: the main tools and techniques used in the study for development and programming tasks. Explanation of their characteristics and what they have contributed to the work.
    \item Conclusions: critical assessment of the research results.
\end{itemize}